%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Server}{August 2023 -- Present}
      {Cypriana}{Roland Park, MD}
      \resumeItemListStart
        \resumeItem{Provided high-quality service to elite guests, such as US senators and political candidates.}
        \resumeItem{Consistently received 5 star reviews and averaged over 20\% on tips.}
        \resumeItem{Welcomed and mentored new team members.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Coding Club Workshop Supervisor}{June 2022}
      {Carroll County Public Library -- Westminster Branch}{Westminster, MD}
      \resumeItemListStart
        \resumeItem{Assisted a week-long coding workshop for middle and high schoolers.}
        \resumeItem{Provided one-on-one guidance and supported the participants as they worked through coding exercises and projects, leading to a 100\% completion rate for all 30 coding exercises.}
        \resumeItem{Acted as a mentor and role model for 30 aspiring programmers by fostering a positive and inclusive learning environment.}
    \resumeItemListEnd

    \resumeSubheading
      {To-Go Specialist}{August 2018 -- June 2023}
      {Olive Garden}{Westminster, MD}
      \resumeItemListStart
        \resumeItem{Delivered exceptional customer service, contributing to our 99\% on-time delivery and 99\% order accuracy.}
        \resumeItem{Successfully onboarded and trained 15-20 new team members, ensuring their seamless integration into the team and adherence to company standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
